Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-04 krs-survey.tex
Various minor changes

Besides, we have decided to restraint the set of systems to those actually
implemented on robots, and used in semantic-rich environments (\ie , dynamic,
partially unknown environments with a large range of different entities which
may have interactions). The typical scenario that would involve such robots is
a service robot in a human-friendly environment like a kitchen.

We have limited ourselves to systems that
\begin{inparaenum} 
    \item  run on \emph{service robot} (that is, robots that interact with 
    objects in a semantic-rich environment primarly designed for humans),
    \item  ground the knowledge in the physical world (physically embedded
    systems able to assess their environment),
    \item  are able to merge different knowledge modalities,
    \item  are endowed with on-line, dynamic reasoning (\ie not a simple static
    database).
\end{inparaenum}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Prototypical Scenario}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A typology of features of KRS for robotics}
\label{sect|features}

The previous section detailed an imaginary cooking scenario. We identified, in
no particular order, numerous desirable features for a knowledge representation
system for robotics.

@@

\fxnote{Should we also mention the general dynamics of the knowledge
representation system? ie, the system from the point of view of an on-going
cognitive process. See \cite{Henderson2011}}

@@

>>>>

Besides, we have decided to restraint the set of systems to those actually
implemented on robots, and used in semantic-rich environments (\ie , dynamic,
partially unknown environments with a large range of different entities which
may have interactions). The typical scenario that would involve such robots is
a service robot in a human-friendly environment like a kitchen (as described in
section~\ref{sect|scenario}).

We have limited ourselves to systems that
\begin{inparaenum} 
    \item  run on \emph{service robot} (that is, robots that interact with 
    objects in a semantic-rich environment primarly designed for humans),
    \item  ground the knowledge in the physical world (physically embedded
    systems able to assess their environment),
    \item  are able to merge different knowledge modalities,
    \item  are able of on-line, dynamic knowledge acquisition and reasoning 
    (\ie not a simple static database).
\end{inparaenum}

This exclude \textit{de facto} classical cognitive systems like {\sc Soar} or
{\sc ACT-R} for which we could not find recent implementations on full-scale
service robots.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Prototypical Scenario}
\label{sect|scenario}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Typology of Knowledge Representation Systems Requirements for Robotics}
\label{sect|features}

We have detailed an imaginary cooking scenario where numerous desirable
features for a knowledge representation system for robotics have been
identified in no particular order.

@@

@@

\subsubsection{Memory}
\label{sect|memory}
